\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
 
\usepackage[usenames, dvipsnames]{color}

\begin{document}
%----------------------
\textbf{Task 1: Single Supporting Fact}

\begin{itemize}

	\item[1.] Mary went to the bathroom.
	\item[2.] John moved to the hallway.
	\item[3.] Mary traveled to the office.

\end{itemize}

\textcolor{blue}{Q}: Where is Mary?
\textcolor{red}{A: office} \\
%----------------------

%----------------------
\textbf{Task 2: Two Supporting Facts}

\begin{itemize}

	\item[1.] John is in the playground.
	\item[2.] John picked up the football.
	\item[3.] Bob went to the kitchen.

\end{itemize}

\textcolor{blue}{Q}: Where is the football?
\textcolor{red}{A: playground} \\
%----------------------

%----------------------
\textbf{Task 3: Three Supporting Facts}

\begin{itemize}

	\item[1.] John picked up the apple.
	\item[2.] John went to the office.
	\item[3.] John went to the kitchen.
	\item[4.] John dropped the apple.

\end{itemize}

\textcolor{blue}{Q}: Where was the apple before the kitchen?
\textcolor{red}{A: office}\\
%----------------------

\pagebreak

%----------------------
\textbf{Task 4: Two Argument Relations}

\begin{itemize}

	\item[1.] The office is north of the bedroom.
	\item[2.] The bedroom is north of the badroom.
	\item[3.] The kitchen is west of the graden.

\end{itemize}

\textcolor{blue}{Q}: What is the north of the bedroom?
\textcolor{red}{A: office}

\textcolor{blue}{Q}: What is the bedroom north of?
\textcolor{red}{A: badroom}\\
%----------------------


%----------------------
\textbf{Task 5: Yes/No questions}

\begin{itemize}

	\item[1.] John moved to the playground.
	\item[2.] Daniel went to the bathroom.
	\item[3.] John went back to the hallway.

\end{itemize}

\textcolor{blue}{Q}: Is John in the playground?
\textcolor{red}{A: no}

\textcolor{blue}{Q}: Is Daniel in the bathroom?
\textcolor{red}{A: yes}\\
%----------------------

%----------------------
\textbf{Task 6: Counting}

\begin{itemize}

	\item[1.] Daniel picked up the football.
	\item[2.] Daniel dropped up the football.
	\item[3.] Daniel got milk.
	\item[4.] Daniel took the apple.

\end{itemize}

\textcolor{blue}{Q}: How many objects is Daniel Holding?
\textcolor{red}{A: two} \\
%----------------------


%---------------------------
\end{document}